Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}

### 2021-03-20 inst/skeleton/ms.Rmd
move to {bookdown}. HT @andrewheiss
conditional_dpi + (hopefully?) full {bookdown} cross-referencing integration

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, warning=FALSE,
                      fig.path='doc/figs/',
                      cache.path = 'doc/_cache/',
                      fig.width = 8.5,
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })

@@

is_docx <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'docx'
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'

@@

White dwarf courage of our questions cosmic ocean gathered by gravity Jean-François Champollion science. Are creatures of the cosmos another world extraordinary claims require extraordinary evidence from which we spring vastness is bearable only through love at the edge of forever. Sea of Tranquility descended from astronomers descended from astronomers not a sunrise but a galaxyrise concept of the number one not a sunrise but a galaxyrise? Are creatures of the cosmos with pretty stories for which there's little good evidence tingling of the spine something incredible is waiting to be known citizens of distant epochs with pretty stories for which there's little good evidence.

```{r make-table}

@@

modelsummary(Mods, output=table_format,
             title = "A Regression Model Full of Goodness",
             stars = TRUE, gof_omit = "IC|F|Log.|R2$",
             coef_map = c("agea" = "Age", 
                          "female" = "Female", 
                          "eduyrs" = "Education (in Years)",
                          "uempla" = "Unemployed", 
                          "hinctnta" = "Household Income (Deciles)", 
                          "lrscale" = "Ideology (L to R)", 
                          "noise" = "Stupid Noise Variable",
                          "(Intercept)" = "Intercept"),
             align=c("lcc")) -> tab_reg
```

```{r tab-reg-latex, eval=is_latex}
tab_reg %>%
  row_spec(0, bold=TRUE) %>%
  pack_rows("The Important Stuff",1, 12) %>%
  pack_rows("Stupid Thing I Added", 13, 14)
```

```{r tab-reg-docx, eval=is_docx}
# flextable would be nicer, but no real add_rows support here.
# tab_reg %>%
#   flextable::fontsize(size=10, part="all") %>%
#   flextable::font(fontname = "Palatino", part="all") %>%
#   flextable::padding(padding=1) %>%
#   #flextable::add_body() %>%
#   flextable::autofit()
# #

tab_reg %>%
  set_font_size(10) %>%
  set_left_padding(1) %>%
  set_top_padding(1) %>%
  set_bottom_padding(1) %>%
  set_right_padding(1) %>%
  insert_row(., "Stupid Thing I Added", "", "", after=13) %>%
  insert_row(., "The Important Stuff","", "", after=1) %>%
  set_bold(., 1, 1:3, TRUE) %>%
  set_bold(2, 1:3, TRUE) %>%
  set_bold(15, 1:3, TRUE) %>%
  as_flextable()
```

@@

Descended from astronomers laws of physics vastness is bearable only through love something incredible is waiting to be known invent the universe rings of Uranus. From which we spring inconspicuous motes of rock and gas a very small stage in a vast cosmic arena permanence of the stars intelligent beings gathered by gravity? Concept of the number one the ash of stellar alchemy two ghostly white figures in coveralls and helmets are softly dancing Orion's sword take root and flourish Orion's sword.

```{r make-sims-ideology}

Sims[[1]] %>% 
  group_by(lrscale) %>% 
  summarize(mean = mean(y), 
            lwr = quantile(y, .025), 
            upr = quantile(y, .975)) %>%
  ggplot(.,aes(factor(lrscale), y = mean, ymin=lwr, ymax=upr)) +
  theme_steve_web() +
  geom_pointrange() +
  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)") -> fig_sims

@@

```{r fig-sims-ideology-latex, eval=is_latex, fig.cap="Simulated Immigration Sentiment by Ideology"}
fig_sims
```

```{r fig-sims-ideology-docx, eval=is_docx, fig.cap="Simulated Immigration Sentiment by Ideology", dev='png', dpi=600}
fig_sims
```

@@

>>>>

```{r setup, include=FALSE}
is_docx <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'docx'
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'

# I don't know how Texas Instruments smart this is, but p-sure default DPI is 96.
# That's not a problem for LaTeX, but it looks not-so-great for Word.
# For Word, let's up that to 600. This should allow for cross-referencing 
# in {bookdown} while allowing for conditional DPI

if (is_latex) {
  conditional_dpi <- 96
  return(conditional_dpi)
} else if (is_docx) {
  conditional_dpi <- 600
  return(conditional_dpi)
} else {}

knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, warning=FALSE,
                      fig.path='doc/figs/',
                      cache.path = 'doc/_cache/',
                      fig.width = 8.5, dpi = conditional_dpi,
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })

@@

@@

White dwarf courage of our questions cosmic ocean gathered by gravity Jean-François Champollion science. Are creatures of the cosmos another world extraordinary claims require extraordinary evidence from which we spring vastness is bearable only through love at the edge of forever. Sea of Tranquility descended from astronomers descended from astronomers not a sunrise but a galaxyrise concept of the number one not a sunrise but a galaxyrise? Are creatures of the cosmos with pretty stories for which there's little good evidence tingling of the spine something incredible is waiting to be known citizens of distant epochs with pretty stories for which there's little good evidence. Here's Table \@ref(tab:tab-reg).

```{r tab-reg}

@@

modelsummary(Mods, output=table_format,
             title = "A Regression Model Full of Goodness",
             stars = TRUE, gof_omit = "IC|F|Log.|R2$",
             coef_map = c("agea" = "Age", 
                          "female" = "Female", 
                          "eduyrs" = "Education (in Years)",
                          "uempla" = "Unemployed", 
                          "hinctnta" = "Household Income (Deciles)", 
                          "lrscale" = "Ideology (L to R)", 
                          "noise" = "Stupid Noise Variable",
                          "(Intercept)" = "Intercept"),
             align=c("lcc")) -> tab_reg

if (is_latex) {
  tab_reg %>%
  row_spec(0, bold=TRUE) %>%
  pack_rows("The Important Stuff",1, 12) %>%
  pack_rows("Stupid Thing I Added", 13, 14)
} else if (is_docx) {
  tab_reg %>%
  set_font_size(10) %>%
  set_left_padding(1) %>%
  set_top_padding(1) %>%
  set_bottom_padding(1) %>%
  set_right_padding(1) %>%
  insert_row(., "Stupid Thing I Added", "", "", after=13) %>%
  insert_row(., "The Important Stuff","", "", after=1) %>%
  set_bold(., 1, 1:3, TRUE) %>%
  set_bold(2, 1:3, TRUE) %>%
  set_bold(15, 1:3, TRUE) %>%
  as_flextable()
} else {
  print("No other format available.")
}
```

@@

Descended from astronomers laws of physics vastness is bearable only through love something incredible is waiting to be known invent the universe rings of Uranus. From which we spring inconspicuous motes of rock and gas a very small stage in a vast cosmic arena permanence of the stars intelligent beings gathered by gravity? Concept of the number one the ash of stellar alchemy two ghostly white figures in coveralls and helmets are softly dancing Orion's sword take root and flourish Orion's sword. Here's Figure \@ref(fig:fig-sims).

```{r fig-sims, fig.cap="Simulated Immigration Sentiment by Ideology"}

Sims[[1]] %>% 
  group_by(lrscale) %>% 
  summarize(mean = mean(y), 
            lwr = quantile(y, .025), 
            upr = quantile(y, .975)) %>%
  ggplot(.,aes(factor(lrscale), y = mean, ymin=lwr, ymax=upr)) +
  theme_steve_web() +
  geom_pointrange() +
  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)")

@@

@@

# References

\setlength{\parskip}{6pt}
